### 2016-11-08 datamining/summery.tex
summery stuff

\pdfinfo{
  /Title (EC cheatsheet)
  /Creator (TeX)
  /Producer (pdfTeX 1.40.0)
  /Author (Jappie Klooster)
  /Subject (Evulotionary computing)
  /Keywords (Evolutionary, Computing, Gentic, Algorithm, Heuristics, Strategy)}

@@

\subsection{Missing data}
The easiest way is  to throw away records with missing data.
This has the following disadvantages: Potential bias and loss of power (which
means that our precision is reduced because we loose a lot of examples).
If we want to use a tree with incomplete data we have the following problems:
How to determine the quality of a spiet? Which way gets an observation send
with a missing value?
If the class labe misses its useless anyway so it should be thrown away.
A solution is ignoring the quality aspect and add surogate splits.
\subsection{Computational efficiency}
A categorical attribute with $L$ is distinct values has $2^{L-1}-1$ possible
distinct splits.
For binary class problems and impurity measures that belong to class $\mathcal{F}$
there is a more efficient algorithm for finding the optimal split.
$p(0|x=b_l)$  denotes the realitve frequency of class 0 for observations in the
current node with $x=b_l$. Order $p(0|x=b_l)$. Then one of the $L$ subsets
is the optimal split. Thus the search is reduced to $O(L-1)$
\subsubsection{Tree construction}
   Asuming all $p$ attributes $x_1, ..., x_p$ are numeric we have to sort
   them per attribute, which takes $O(n log n)$ time.
   Best case (where each split is a perfect subdivision) we traverse the tree
   and have to consider $O(n)$ splits per level resulting in $O(n log n)$ time.
   Worst case it becomes $O(n^2)$
\section{Graphical models}
\subsection{Probability rules}
sum rule $P(X)=\sum_y P(X,Y)$, product rule $P(X,Y)=P(X|Y)P(Y)$.
\subsection{Independence}
Random vectors $X$ and $Y$ are independent iff $P(x,y)=P(x)P(y) \text{ for all } (x,y)$
Therefore $P(x|y)=P(x)$. Independence can be written as $X \indep Y$
\section{Baysian networks}
\section{Freq item set mining}
\end{multicols}
\end{document}

>>>>

\pdfinfo{
  /Title (Datamining cheatsheet)
  /Creator (TeX)
  /Producer (pdfTeX 1.40.0)
  /Author (Jappie Klooster)
  /Subject (Evulotionary computing)
  /Keywords (Evolutionary, Computing, Gentic, Algorithm, Heuristics, Strategy)}

@@

\subsection{Missing data}
The easiest way is  to throw away records with missing data.
This has the following disadvantages: Potential bias and loss of power (which
means that our precision is reduced because we loose a lot of examples).
If we want to use a tree with incomplete data we have the following problems:
How to determine the quality of a spiet? Which way gets an observation send
with a missing value?
If the class labe misses its useless anyway so it should be thrown away.
A solution is ignoring the quality aspect and add surogate splits.
\subsection{Computational efficiency}
A categorical attribute with $L$ is distinct values has $2^{L-1}-1$ possible
distinct splits.
For binary class problems and impurity measures that belong to class $\mathcal{F}$
there is a more efficient algorithm for finding the optimal split.
$p(0|x=b_l)$  denotes the realitve frequency of class 0 for observations in the
current node with $x=b_l$. Order $p(0|x=b_l)$. Then one of the $L$ subsets
is the optimal split. Thus the search is reduced to $O(L-1)$
\subsubsection{Tree construction}
   Asuming all $p$ attributes $x_1, ..., x_p$ are numeric we have to sort
   them per attribute, which takes $O(n log n)$ time.
   Best case (where each split is a perfect subdivision) we traverse the tree
   and have to consider $O(n)$ splits per level resulting in $O(n log n)$ time.
   Worst case it becomes $O(n^2)$
\section{Graphical models}
\subsection{Probability rules}
sum rule $P(X)=\sum_y P(X,Y)$, product rule $P(X,Y)=P(X|Y)P(Y)$.
To estimate the joint distrubtion of $X$ and $Y$ we use $\overset{\wedge}{P}(x,y)=\frac{n(x,y)}{n}$
\subsection{Independence}
Random vectors $X$ and $Y$ are independent iff $P(x,y)=P(x)P(y) \text{ for all } (x,y)$
Therefore $P(x|y)=P(x)$. Independence can be written as $X \indep Y$.
This gives the factorisation criterion for independent randomvectors:
random vectors $X$ and $Y$ are independent iff there exists two functions $g$
and $h$ such that: $P(x,y) = g(x)h(y)$ for all $(x,y)$.
Random vectors $X$ and $Y$ re independent given $Z$ iff
$P(x,y,z)=P(x,z)P(y,z)/P(z)$.
\section{Baysian networks}
\section{Freq item set mining}
\end{multicols}
\end{document}
